---
title: "trapinch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trapinch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(httptest2)
start_vignette("readme")
```

```{r setup}
library(trapinch)
```


Calls are in the form {base URL}/{endpoint}/{resource}. 

No authorisation is required to use the API.

Results are paged, but the {trapinch} package requests all resources for a given endpoint at once.

There's one case, for Pokémon encounters data, that extends the path to {base URL}/{endpoint}/{resource}/{ext}, which can only be used in the form {base URL}/pokemon/{resource}/encounters.

An empty call returns all resources for the given endpoint.

Calls are cached in the directory resolved by `tools::R_user_dir(, which = "cache")` on your machine. The data returned from the first call to the API is cached; the data is retrieved from that cache when that same request is made again.


```{r, include=FALSE}
end_vignette()
```
